Reviewer Comments (Scientific Reports)

### 2020-01-24 notebook/sci_rep_reviews.Rmd
Respond to reviewer 1's comments

Reviewer 1 comments
================================================================================

@@

@@

@@

@@

>>>>

Reviewer 1 comment 1
================================================================================

@@

Author response to Reviewer 1 comment 1
================================================================================

I thank the reviewer for these comments. I share their belief that the issues in this paper are of current concern in ecology, and that the ideas presented in this manuscript are, to the best of my knowledge, novel.

Reviewer 1 comment 2
================================================================================

@@

Author response to Reviewer 1 comment 2
================================================================================

I again thank the reviewer for their comments. I agree that it is especially relevant that my manuscript focuses on finite S values, and I have made more emphasis on this point in my revision (line XXX).

Reviewer 1 comment 3
================================================================================

@@

Author response to Reviewer 1 comment 3
================================================================================

I agree with the relevance of Dougoud et al. (2018), and have made appropriate links to their results on feasibility. Nevertheless, one major result of my manuscript is that varying component response rates (i.e., $\gamma$) only affect stability, not feasibility. Hence, Reviewer 1 is incorrect that my conclusions concerning varying component response rates should be expected to enhance feasibility in experimentally observed food webs (and therefore that stability should be enhanced for biologically realistic systems in which all population densities are positive). Checking for validity in empirical food webs is therefore not entirely appropriate because the consequences of such an investigation would have negligible practical application.

I welcome Reviewer 1's call for expanding the scope of models considered for simulations, which was also recommended by Reviewer 2. Nevertheless, my manuscript focuses broadly on complex systems rather than pure ecological systems, so I have revised my manuscript to test more general models of common network structures. In terms of ecological models, in addition to random competition, mutualism, and predator-prey networks, I have now also included a cascade food web model (which is a foundation for the extended niche and nested-heirarchy models that Reviewer 1 mentions; Williams and Martinez 2000). Other network types that I have incorporated into my revision include small-world networks (Watts and Strogatz 1998) and scale-free networks (Albert and Barab\'{a}si 2002). Overall, the structured networks that I now include in the main text and supporting information now encompass a wide range of physical, biological, and social systems.

More emphasis on feasibility and how it relates to ecological systems has now been included (line XXX). I have also added new sections in the Results (line XXX) and methods (line XXX) for the new simulations of structured networks. Full details of these results have also been added to the supporting information, and code for building structured networks is publicly available as a documented R package on GitHub (https://github.com/bradduthie/RandomMatrixStability).

Reviewer 1 comment 4
================================================================================

@@

Author response to Reviewer 1 comment 3
================================================================================

Reviewer 1 is correct that the line illustrates the conditional probability that $A$ is unstable given that $\gamma A$ is stable. In other words, the proportion of complex systems found to be stable, but which would have been unstable if it were not for the variation in component response rates.

I have explained the result shown by the black line of Figures 3 and 4 now more clearly in my revision (line XXX).
